Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Fig 4: Caption

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
      \caption{
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	  galaxies in halos less massive than $10^{14} M_{\odot}$ (grey dots) and 
      	  in halos more massive than $10^{14} M_{\odot}$ (red squares). 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for galaxies with
          $11.6<$\logmtot{}$<11.9$. 
          \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
          function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
          of the total luminosity whereas solid lines correspond to the SMF computed
          using the total luminosity from our 1-D profile. 
          The impact on the SMF can exceed 0.2 dex for massive central galaxies 
          living in halos larger than $\log (M_{\mathrm{halo}}/M_{\odot}) > 14.2$ 
          (red lines).
          \song{New figure for completeness; Need to update the caption}
          }
      \label{fig:mass_complete}
  \end{figure}

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_completeness}
      \caption{
          Evaluation of the \mstar{} completeness of the HSC massive galaxy sample.
          We compare the volume number density function of the massive galaxies 
          for this work (black line) with the one of a much more complete sample
          from the S82-MGC catalog (green line).  
          The associated uncertainties derived from bootstrap resampling are shown in 
          shaded regions. 
          The vertical grey line highlight the \logms{}$=11.6$ limit.  
          Below it, the HSC massive galaxy sample becomes significantly incomplete in 
          stellar mass. 
          }
      \label{fig:mass_complete}
  \end{figure}
